Distinction Centrality Analysis

### 2025-07-31 analysis.qmd
now new and improved
ok NOW it's the real deal

```{r Toy Examples}
   source(here("Functions", "distinction.R"))
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- g1 + edge(2,3)
   g10 <- g10 + edge(3,4)
   g10 <- g10 + edge(4,5)
   g10 <- g10 + edge(5,6)
   g10 <- g10 + edge(6,7)
   g10 <- g10 + edge(7,2) #wheel graph
   g11 <- make_ring(8) 
   g11 <- delete_vertices(g11, 8) #path graph
```

```{r}
   source(here("Functions", "distinction.R"))
   distinction(g11, norm = "one")
```

>>>>

```{r Toy Examples}
   source(here("Functions", "distinction.R"))
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- g1 + edge(2,3)
   g10 <- g10 + edge(3,4)
   g10 <- g10 + edge(4,5)
   g10 <- g10 + edge(5,6)
   g10 <- g10 + edge(6,7)
   g10 <- g10 + edge(7,2) #wheel graph
   g11 <- make_ring(8) 
   g11 <- delete_vertices(g11, 8) #path graph
   distinction(g11)
```
